\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-31 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Graph

\begin{figure}[!h]
    \centering
    \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
        \caption{\small}
    \end{subfigure}
    \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
        \caption{\small}
    \end{subfigure}
    \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
        \caption{\small}
    \end{subfigure}
     \begin{subfigure}[!h]{0.49\textwidth}
        \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
        \caption{\small}
    \end{subfigure}
    \caption{A schematic to represent orthogonal and oblique reconciliation.  Orange colour points in top left figure represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection_new}
\end{figure}

>>>>

\begin{figure}[!h]
    \centering
    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
        \caption{}
    \end{subfigure}
    \caption{A schematic to represent orthogonal and oblique reconciliation.  Orange colour points in top left figure represent the insample errors.$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection. } \label{fig:OthogonalVSOblique_projection_new}
\end{figure}
